%Acknowledgements

\section{Preface}



%
%\begin{itemize}
%	\item Sune Olander Rasmussen.
%	\item Office comrades: Mika, Niels, Lisa, Andrew, Camilla...
%	%\item Lisbeth Tangaa Nielsen, Ben Keisling, Iben Koldtoft.
%\end{itemize}


\noindent\textbf{Zheming (Kian) Gao} \\

\noindent\emph{University:} University of Copenhagen\\
\emph{Institute:} Niels Bohr Institute\\
\emph{Department:} Centre for Quantum Devices\\
%\emph{Author:} Martin Vindbæk Madsen\\
\emph{E-mail:} gao\_zm87@yahoo.com\\
\emph{KU-username:} shp593\\
\emph{Title:} Towards tantalum superonducting qubits with shadowed junction nanowires\\
%\emph{Academic advisors:} Hans Christian Steen-Larsen and Dorthe Dahl-Jensen, Center for Ice and Climate.\\
\emph{Submitted:} \today
%\begin{itemize}
	%\item  
	%\item EC: Jason Box GEUS + Alan Hubbard Aberystwith University
	%\item Aerodynamic profilers -- cup anemometers and fine wire thermocouples Jason Box GEUS
	%\item I want to acknowledge the use of data obtained from \cite{Bamber2003}
	%\item Usage of data: PROMICE
	%\item who measured the isotopes of the snow samples? And what instrument was used? AWI? With whom did we collaborate with the snow surface protocol?
%\end{itemize}
\clearpage
\section{Acknowledgements}

The lovely people in the QDev are like sunlight shining on my journey. My supervisor, Morten Kjærgaard, you are the most superb supervisor in my heart. I still remember that the first time I entered your office, with anxiety and fear, your passion and encouragement motivated me to enter the quantum field. Your full support of our ideas and experiments inspires me to continually crank the challenging tasks and generate more brilliant thoughts. Thank you for guiding me into this fascinating field. Zhenhai, you are the hero in my heart. Whether fabricating chips on the weekend, setting up instruments, or fetching data from measurements, you always assist me without complaint, even if I do things wrong. Thank you for being my strong back. A big thanks to Smitha for helping me in developing recipes and fabricating devices. I'm sorry to bother you during weekends and even your vacation a few times, but I won't stop calling you when I'm in trouble. Thank you, Michaela, for the assistance on fabrication and the energetic conversation on technology. It is hard to get hygge on recipe development and designing without you. Thank you, Jose, for sharing your thoughts and experience on measurement; that really helps a lot in my focus while measuring. Thank you Sangeeth, for helping with fabrication and the brilliant ideas for making devices. Thank Asbjørn, for all sorts of help on theory, instruments, and data analysis. Serwan, thank you for the useful discussion on theory. I hope we can still do frequently climbing in the future. Thanks to my mate Will, for helping me with understanding some weird behaviors in the data. in Thank Harry for helping with fabrication, instruments, and happiness. Thank Martin, for training me on AFM and providing useful information on your tantalum nanowires. Thank Zhe for training me on Elionix and recipe development. Thank you Karolis and Nader, on my training in many instruments. Thank Henry, for helping with fixing measurement tools. Thank all the cleanroom users, Shuangyue, Stavarolor, and Jordan, for assisting in my fabrication and maintaining a relaxed atmosphere in the cleanroom. A big thanks to our center's director Charles Marcus for the well-arranged, lovely laboratory and useful experiment habits. Thanks to the technical team for maintaining the fabrication and measurement tools.

My mother, Zhidong, my father, Jianguo, and my sister Jingyi, thank you for supporting my study financially and mentally. I always love you.